Computing in the Field of Rationals

### 2012-06-26 rational_ext.tex
_

%%%%%%%%%%%%%%%%%%%
\subsection{Constructions}

@@

% Note that this language is not logically reversible.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions}

@@

\begin{definition}[eval(c,v)]

Given a combinator {{c:b1<->b2}} and a value {{v:b1}} we can define
{{eval(c, v)}} to be the set of values {{v':b}} such that there is
small-step reduction sequence {{c v |-->* v'}}.

$eval(c, v) = \{v'~|~ c~ v\mapsto^{\asterix} v' \} $
\end{definition}

The definition of equality between combinators has to be extended to
reflect the fact that combinators can have multiple outputs for an
input. More generally, combinators denotes relations.

\begin{definition}[c1 = c2]
We say that {{c1 = c2}}, for combinators {{c1:b1<->b2}} and
{{c2:b1<->b2}} iff the denote the same relation between sets {{b1}}
and {{b2}}. Equivalently,

{{forall v:b1. eval(c1, v) = eval(c2, v)}}
\end{definition}

\begin{proposition}[Logical Reversibility]
\label{prop:logrev2}

{{c v |-->* v'}} iff {{ c{dagger} v' |-->* v}}
\end{proposition}

The logical reversibility is extended to relations and should be
understood as follows. The combinator {{c:b1<->b2}} denotes a relation
from {{b1}} to {{b2}} and its adjoint denotes the inverse relation
from {{b2}} to {{b1}}. Operationally, for any execution path from
{{v}} to {{v'}} in {{c}}, {{c{dagger} }} has an execution path from
{{v'}} to {{v}}.

\roshan{This is an important question -- is {{PiEE*}} still
  bimonoidal? i.e. so all the coherence conditions on isomorphisms
  naturally extend to relations. I suspect yes.}
